---
title: <span style="color:#E95420">***PrescRiptions Report - `r params$monthTitle`***</span>
pagetitle: "PrescRiptions Report `r params$monthTitle`"
output:
  html_document:
    theme: united
    highlight: default
    df_print: paged
    toc: true
    toc_depth: 4
    toc_float: 
      collapsed: true
      smooth_scroll: true
    number_sections: false
  fig_caption: true
  includes:
    in_header: header.tex
  keep_tex: true
  pandoc_args: --tab-stop=2
  # bookdown::pdf_book:
  #   df_print: paged
  #   toc: true
  #   toc_depth: 4
  #   number_sections: false
params:
  year: year,
  month: month,
  monthName: NameMonth,
  monthTitle: monthTitle
  prefix: prefix
  geoArea: geo  
  selccg: ccg  
  selgp: gp  
  outputFolder: outFolder
  inputFolder: inputFolder
  monthData: monthData
  settings: settings
header-includes:
- \usepackage{makeidx}
- \makeindex
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h
- \usepackage{amsmath}
- \usepackage{amssymb}
- \usepackage{amsthm}
- \usepackage{mathtools}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
ggplot2::theme_set(ggthemes::theme_economist()) # Sets graphs themes to "The Economist" style
```

```{r dataImport, include=FALSE, echo=FALSE}

for (i in 1:length(params$monthData)){
  # print(names(dataAll)[i])
  assign(gsub("[[:digit:]]|_","",names(monthData))[i],params$monthData[[i]])
}

bnf[,BNF.Presentation.Code:=as.character(BNF.Presentation.Code)]


regionPrescriptions = PrescRiptions::generateSummaries(plpd,bnf,on = "REGION",params$settings)
bnfPrescriptions = PrescRiptions::generateSummaries(plpd,bnf,on = "BNF",params$settings)


## CCGs

ccgSum = ccgSummaries(plpd,bnf,demog,demogMap,params$settings)

ccg_summary = ccgSum$ccg_summary %>%
  data.table

ccg_bnf = ccgSum$ccg_bnf %>%
  data.table

ccg_aggr= ccgSum$ccg_aggr %>%
  mutate(NIC_RATE_Z=scale(NIC_RATE)[,]) %>%
mutate(NIC_RATE_Z_TYPE=ifelse(NIC_RATE_Z < -1, "Cost Below Average", ifelse(NIC_RATE_Z < 1, "Average Cost", "Cost Above Average"))) %>%
data.table

ccg_summaryC = ccg_summary %>%
  dplyr::filter(ONS_CCG_CODE == params$selccg) %>%
  data.table

ccg_bnfC = ccg_bnf %>%
  dplyr::filter(ONS_CCG_CODE == params$selccg)%>%
  data.table

ccg_aggrC= ccg_aggr %>%
  dplyr::filter(ONS_CCG_CODE == params$selccg)%>%
  data.table

# GPs

gpSum = gpSummaries(plpd,demog,demogMap,params$settings)

gpSumC = gpSum %>%
  dplyr::filter(PRACTICE == params$selgp)%>%
  data.table

gpSum[,NIC_RATE := round(NIC_RATE,2)]
gpCostlier = gpSum[NIC_RATE_Z >2,2:8]

gpSumT = copy(gpSum)

data.table::setDT(gpSumT)[, (colnames(gpSumT)):= lapply(.SD, function(x) format(x,big.mark = ".",decimal.mark = ",",scientific = FALSE)),
                         .SDcols = colnames(gpSumT)]


gpC = plpd[PRACTICE == params$selgp]
gpC[,REGION:="Practice"]
# bnf[,BNF.Presentation.Code:=as.character(BNF.Presentation.Code)]
gpC = data.table(left_join(gpC, bnf, by = c("BNF.CODE" = "BNF.Presentation.Code")))

groupVar3 <- c("PERIOD", "PRACTICE")
measures <- c("ITEMS","NIC", "ACT.COST", "QUANTITY", "PERIOD", "PRACTICE", "BNF.CODE" )

gpCsum <-  gpC %>%
  dplyr::select(PERIOD,all_of(measures)) %>%
  dplyr::group_by_at(groupVar3) %>%
  dplyr::summarise(ITEMS = sum(ITEMS), NIC = sum(NIC), ACT.COST = sum(ACT.COST), QUANTITY = sum(QUANTITY))%>%
  data.table 

groupVar2 <- c("PERIOD", "PRACTICE", "BNF.Chapter")

gpCsumCode <-  gpC %>%
  dplyr::select(PERIOD,all_of(measures), BNF.Chapter, BNF.Chapter.Code) %>%
  dplyr::group_by_at(groupVar2) %>%
  dplyr::summarise(ITEMS = sum(ITEMS), NIC = sum(NIC), ACT.COST = sum(ACT.COST), QUANTITY = sum(QUANTITY))%>%
  data.table 


gpSum = gpSum[!is.na(NIC_RATE_Z)]
gpSum = gpSum %>%
  mutate(NIC_RATE_Z=scale(NIC_RATE)[,]) %>%
mutate(NIC_RATE_Z_TYPE=ifelse(NIC_RATE_Z < -1, "Cost Below Average", ifelse(NIC_RATE_Z < 1, "Average Cost", "Cost Above Average"))) %>%
  data.table

gpSum[PRACTICE==params$selgp,NIC_RATE_Z_TYPE:="Cost for selected GP"]

Sys.setlocale("LC_TIME", "English")

if(nrow(plpd)<=500000){
  Psample="YES"
}

if(Psample=="YES"){
  dataSample = "SAMPLE PLPD DATA (500.000 ROWS)"
  m1Sample = "complete data"
  m2Sample = "sample = FALSE"
}else{
    dataSample = "TOTAL PLPD DATA"
  m1Sample = "sample data"
  m2Sample = "sample = TRUE"
}

```
<span style="color:#E95420"><font size="5">Authors: *Cristina Muschitiello* - *Niccolò Stamboglis*</font></span>

<span style="color:#E95420"><font size="4">**e-Rum2020** - 20th June 2020</font></span>


***`r format(Sys.time(), '%e %B %Y')`***

This document is automatically generated using the package **PrescRiptions**.
It is composed of the following sections: 

  + **Report By Region**: <span style="background-color:#00FFFF"> ***`r params$geoArea ` - `r params$monthTitle `*** </span>: Summary section for the Region.

  + **Report By CCG (customised section)**:  <span style="background-color:#ffef00"> *CCG `r params$selccg`-`r params$monthTitle `*</span>: customised Section by CCG.

  + **Report By GP (customised section)**:  <span style="background-color:#33ff33"> *GP `r params$selgp`-`r params$monthTitle `*</span>: customised section by GP.

**All the analyses have been run on <span style="color:#E95420">`r dataSample `</span>. For `r m1Sample ` data, set** ***`r m2Sample `*** **in the** ***monthlyDataImport()*** **function**.


<span style="color:#E95420">------------------------------------------------------------------------------------------------------------------------------------------------------------------------------</span>


# ***Report by Region*** 

<span style="background-color:#00FFFF"> <font size="5">***`r params$geoArea ` - `r params$monthTitle `*** </font></span>

## **Summary**

In `r params$geoArea` during `r params$monthTitle ` the following numbers were registered:

```{r table1,  include=TRUE}

numCols = colnames(regionPrescriptions)

data.table::setDT(regionPrescriptions)[, (numCols):= lapply(.SD, function(x) format(x,big.mark = ".",decimal.mark = ",",scientific = FALSE)),
              .SDcols = numCols]

knitr::kable(t(regionPrescriptions[,2:5]),format = "html",
             caption = "Region Numbers") %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header","striped")
                ,bootstrap_options = c("hold_position", "repeat_header","striped", "hover", "condensed", "responsive"),
                full_width = F, position = "left"
  ) 
```

## **Analysis by BNF Code**

### *Summary table* 

The information on prescription at <span style="background-color:#00FFFF">*`r params$geoArea`-`r params$monthTitle `*</span> level by BNF chapter are summarised in the following table

```{r, echo=FALSE, fig.width=8, fig.height=6}
numCols = colnames(bnfPrescriptions)

data.table::setDT(bnfPrescriptions)[, (numCols):= lapply(.SD, function(x) format(x,big.mark = ".",decimal.mark = ",",scientific = FALSE)),
              .SDcols = numCols]

# reactable(bnfPrescriptions[,1:5], paginationType = "jump", defaultPageSize = 6)

```

<!-- seconda opzione tabella -->

```{r table2,  include=TRUE}

knitr::kable(bnfPrescriptions[,1:5],format = "html",caption = paste0(params$geoArea, " - ",params$monthTitle, " by BNF Chapter")) %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header","striped")
                ,bootstrap_options = c("hold_position", "repeat_header","striped", "hover", "condensed", "responsive")
  ) %>%
   kableExtra::scroll_box(height = "350px")
```

### *Prescribed items*

**Prescribed items by BNF code** for <span style="background-color:#00FFFF">*`r params$geoArea`-`r params$monthTitle `*</span> are distributed as follows

```{r, echo=FALSE, fig.width=8, fig.height=6}
bnfPrescriptions = PrescRiptions::generateSummaries(plpd,bnf,on = "BNF",params$settings)

p <- ggplot(bnfPrescriptions, aes(x=reorder(BNF.Chapter, -ITEMS), y=ITEMS)) +
  geom_bar(stat="identity", width=.5, fill="#E95420") +
  labs(title=paste0("Items by BNF Chapter - ",params$geoArea, " - ",params$monthTitle),
       # subtitle="England", 
       caption="source: NHS",
       x="BNF.Chapter") + 
  theme(plot.title = element_text(color="#333333"))+
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 20))+
   scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,angle=90, vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
p

```

### *Actual Costs*

**Actual costs by BNF code** for <span style="background-color:#00FFFF">*`r params$geoArea`-`r params$monthTitle `*</span> are distributed by BNF code as follows

```{r, echo=FALSE, fig.width=8, fig.height=6}
p <- ggplot(bnfPrescriptions, aes(x=reorder(BNF.Chapter, -ACT.COST), y=ACT.COST)) + 
  geom_bar(stat="identity", width=.5, fill="#E95420") + 
  labs(title=paste0("Actual costs by BNF Chapter - ",params$geoArea, " - ",params$monthTitle), 
       # subtitle="England", 
       caption="source: NHS",
       x="BNF.Chapter") + 
    theme(plot.title = element_text(color="#333333"))+
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 20))+
   scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,angle=90, vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
p
```


### *Prescribed quantity*

**Total prescribed quantity by BNF code** for <span style="background-color:#00FFFF">*`r params$geoArea`-`r params$monthTitle `*</span> are distributed by BNF code as follows

```{r, echo=FALSE, fig.width=8, fig.height=6}
p <- ggplot(bnfPrescriptions, aes(x=reorder(BNF.Chapter, -QUANTITY), y=QUANTITY)) + 
  geom_bar(stat="identity", width=.5, fill="#E95420") + 
  labs(title=paste0("Total quantity by BNF Chapter - ",params$geoArea, " - ",params$monthTitle), 
       # subtitle="England", 
       caption="source: NHS",
       x="BNF.Chapter") + 
    theme(plot.title = element_text(color="#333333"))+
scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 20))+
   scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,angle=90, vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
p
```

## **Costs summary by CCG **

This section analyses Net Ingredient Costs per 1K patients in <span style="background-color:#00FFFF">*`r params$geoArea`-`r params$monthTitle `*</span>. Cost analysis might be useful to the NHS for cost-containment.
The figure below provides a graphical representation of Costs by CCG.

```{r, echo=FALSE, fig.width=8, fig.height=6}
ggplot(ccg_aggr, aes(x= NIC_RATE, y= reorder(ONS_CCG_CODE, NIC_RATE))) +
  geom_point(stat='identity', aes(col=NIC_RATE_Z_TYPE), size=2) +
  scale_color_manual(
    values = c("Cost Below Average"="#33ff33", "Average Cost"="#ffef00", "Cost Above Average" = "#E95420")) +
  coord_flip()+
  ggtitle(paste0("Costs per 1K patients by CCG")) +
      theme(plot.title = element_text(color="#333333"))+
xlab("NIC per 1K patients") +
  ylab( "CCG") +
  theme(axis.text.x = element_blank())+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.ticks.x =element_blank())+
  # theme(axis.line.x =element_blank())+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))+
  theme(legend.position = "bottom")+
  theme(legend.title = element_blank())+
  theme(legend.text = element_text(size=9,color="#333333"))

```

## **Costlier GPs**

Below the list of practices who were in the higher end of the distribution of Net Ingredient Cost per 1K patients is reported. More specifically, the table reports the practices with highest NIC per 1K patients, as identified by the practices having a z-score for NIC per 1K patients higher than 2.

The practices reported in the table are the ones which should be considered as reporting an higher-than usual cost per 1K patients. These are practices which should be carefully considered to understand the reasons for their high per capita costs.

```{r, echo=FALSE, fig.width=8, fig.height=6}

data.table::setDT(gpCostlier)[, (colnames(gpCostlier)):= lapply(.SD, function(x) format(x,big.mark = ".",decimal.mark = ",",scientific = FALSE)),
              .SDcols = colnames(gpCostlier)]

if(nrow(gpCostlier)>5){

knitr::kable(gpCostlier,format = "html",
             caption = paste0("COSTLIER PRACTICES - ",params$geoArea, " - ",params$monthTitle)) %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header","striped")
                ,bootstrap_options = c("hold_position", "repeat_header","striped", "hover", "condensed", "responsive")
  ) %>%
   kableExtra::scroll_box(height = "350px")
}else{
  knitr::kable(gpCostlier,format = "html",
             caption = paste0("COSTLIER PRACTICES - ",params$geoArea, " - ",params$monthTitle)) %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header","striped")
                ,bootstrap_options = c("hold_position", "repeat_header","striped", "hover", "condensed", "responsive")
  )
}
```

<span style="color:#E95420">------------------------------------------------------------------------------------------------------------------------------------------------------------------------------</span>

# ***Report by CCG (customised section)*** 
<span style="background-color:#ffef00"> <font size="5">***`r params$selccg` - `r params$monthTitle`*** </font></span>

## **Summary**

```{r,  include=TRUE}

numCols = colnames(ccg_summaryC)

data.table::setDT(ccg_summaryC)[, (numCols):= lapply(.SD, function(x) format(x,big.mark = ".",decimal.mark = ",",scientific = FALSE)),
              .SDcols = numCols]

knitr::kable(t(ccg_summaryC[,3:6]),format = "html",
             caption = paste0("CCG ",params$selccg, " - Summary information")) %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header","striped")
                ,bootstrap_options = c("hold_position", "repeat_header","striped", "hover", "condensed", "responsive"),
                full_width = F, position = "left"
  ) 
```

## **Analysis by BNF Code**

### *Summary table* 

The information on prescription at <span style="background-color:#ffef00"> *CCG `r params$selccg`-`r params$monthTitle `*</span> level by BNF chapter are summarised in the following table

```{r, echo=FALSE, fig.width=8, fig.height=6}
numCols = colnames(ccg_bnfC)

data.table::setDT(ccg_bnfC)[, (numCols):= lapply(.SD, function(x) format(x,big.mark = ".",decimal.mark = ",",scientific = FALSE)),
              .SDcols = numCols]

knitr::kable(ccg_bnfC[,3:7],format = "html",caption = paste0("CCG ",params$selccg, " - ",params$monthTitle, " by BNF Chapter")) %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header","striped")
                ,bootstrap_options = c("hold_position", "repeat_header","striped", "hover", "condensed", "responsive")
  ) %>%
   kableExtra::scroll_box(height = "350px")

```

### *Prescribed items*

**Prescribed items by BNF code** for <span style="background-color:#ffef00"> *CCG `r params$selccg`-`r params$monthTitle `*</span> are distributed as follows

```{r, echo=FALSE, fig.width=8, fig.height=6}

p <- ggplot(ccg_bnf, aes(x=reorder(BNF.Chapter, -ITEMS), y=ITEMS)) +
  geom_bar(stat="identity", width=.5, fill="#E95420") +
  labs(title=paste0("Items by BNF Chapter - ","CCG ",params$selccg, " - ",params$monthTitle),
       # subtitle=paste0("CCG ",params$selccg), 
       caption="source: NHS",
       x="BNF.Chapter") + 
    theme(plot.title = element_text(color="#333333"))+
scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 20))+
   scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,angle=90, vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
p

```

### *Actual Costs*

**Actual costs by BNF code** for <span style="background-color:#ffef00"> *CCG `r params$selccg`-`r params$monthTitle `*</span> are distributed as follows

```{r, echo=FALSE, fig.width=8, fig.height=6}
p <- ggplot(ccg_bnf, aes(x=reorder(BNF.Chapter, -ACT.COST), y=ACT.COST)) + 
  geom_bar(stat="identity", width=.5, fill="#E95420") + 
  labs(title=paste0("Actual costs by BNF Chapter - ","CCG ",params$selccg, " - ",params$monthTitle),
       # subtitle="England", 
       caption="source: NHS",
       x="BNF.Chapter") + 
    theme(plot.title = element_text(color="#333333"))+
scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 20))+
   scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,angle=90, vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
p
```

### *Prescribed quantity*

**Total prescribed quantity by BNF code** for <span style="background-color:#ffef00"> *CCG `r params$selccg`-`r params$monthTitle `*</span> are distributed as follows

```{r, echo=FALSE, fig.width=8, fig.height=6}
p <- ggplot(ccg_bnf, aes(x=reorder(BNF.Chapter, -QUANTITY), y=QUANTITY)) + 
  geom_bar(stat="identity", width=.5, fill="#E95420") + 
  labs(title=paste0("Total quantity by BNF Chapter - ","CCG ",params$selccg, " - ",params$monthTitle),
       # subtitle="England", 
       caption="source: NHS",
       x="BNF.Chapter") + 
    theme(plot.title = element_text(color="#333333"))+
scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 20))+
   scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,angle=90, vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
p
```

## **Cost analysis**

The average NIC per 1K patients in the <span style="background-color:#ffef00"> *CCG `r params$selccg` - `r params$monthTitle `*</span> is **`r round(ccg_aggrC$NIC_RATE,2)`**. This value set the CCG at the **`r names(which(ccg_aggrC$NIC_RATE < quantile(ccg_aggr$NIC_RATE, probs = seq(0, 1, by= 0.1)))[1])`** percentile of the CCG distribution for this indicator.

The figure below provides a graphical comparison of the CCG costs benchmarked with other CCG rates.

```{r, echo=FALSE, fig.width=8, fig.height=6}

ccg_aggr[ONS_CCG_CODE == params$selccg,NIC_RATE_Z_TYPE:="Cost for selected CCG"]

ggplot(ccg_aggr, aes(x= NIC_RATE, y= reorder(ONS_CCG_CODE, NIC_RATE))) +
  geom_point(stat='identity', aes(col=NIC_RATE_Z_TYPE), size=2) +
  scale_color_manual(
    # labels = c("Above Average", "Average", "Below average"),
    values = c("Cost Below Average"="#33ff33", "Average Cost"="#ffef00", "Cost Above Average" = "#E95420","Cost for selected CCG" = "#00FFFF")) +
  coord_flip()+
  ggtitle(paste0("Costs per 1K patients - CCG ",params$selccg)) +
      theme(plot.title = element_text(color="#333333"))+
xlab("NIC per 1K patients") +
  ylab( "CCG") +
  theme(axis.text.x = element_blank())+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.ticks.x =element_blank())+
  # theme(axis.line.x =element_blank())+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))+
  theme(legend.position = "bottom")+
  theme(legend.title = element_blank())+
  theme(legend.text = element_text(size=9,color="#333333"))+
  geom_point(data=ccg_aggrC , aes(x=NIC_RATE, y=ONS_CCG_CODE), colour="#00FFFF", size=3)+
  geom_text(aes(label=ifelse(ONS_CCG_CODE == params$selccg,round(NIC_RATE,3),'')),hjust=0,vjust=-0.8,size=3,color="#333333")



```


<span style="color:#E95420">------------------------------------------------------------------------------------------------------------------------------------------------------------------------------</span>

# ***Report by GP (customised section)*** 
<span style="background-color:#33ff33"> <font size="5">***`r params$selgp` - `r params$monthTitle`*** </font></span>

## **Summary**

```{r,  include=TRUE}

numCols = colnames(gpSumC)

gpSumCT = copy(gpSumC)

data.table::setDT(gpSumCT)[, (numCols):= lapply(.SD, function(x) format(x,big.mark = ".",decimal.mark = ",",scientific = FALSE)),
              .SDcols = numCols]

knitr::kable(t(gpSumCT[,3:6]),format = "html",
             caption = paste0("GP ",params$selgp, " - Summary information")) %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header","striped")
                ,bootstrap_options = c("hold_position", "repeat_header","striped", "hover", "condensed", "responsive"),
                full_width = F, position = "left"
  ) 
```

## **Analysis by BNF Code**

### *Summary table* 

The information on prescription at <span style="background-color:#33ff33"> *GP `r params$selgp`-`r params$monthTitle `*</span> level by BNF chapter are summarised in the following table

```{r, echo=FALSE, fig.width=8, fig.height=6}
numCols = colnames(gpCsumCode)

gpCsumCodeT = copy(gpCsumCode)

data.table::setDT(gpCsumCodeT)[, (numCols):= lapply(.SD, function(x) format(x,big.mark = ".",decimal.mark = ",",scientific = FALSE)),
              .SDcols = numCols]

knitr::kable(gpCsumCodeT[,3:7],format = "html",caption = paste0("GP ",params$selgp, " - ",params$monthTitle, " by BNF Chapter")) %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header","striped")
                ,bootstrap_options = c("hold_position", "repeat_header","striped", "hover", "condensed", "responsive")
  ) %>%
   kableExtra::scroll_box(height = "350px")

```
### *Prescribed items*

**Prescribed items by BNF code** for <span style="background-color:#33ff33"> *GP `r params$selgp`-`r params$monthTitle `*</span> are distributed as follows

```{r, echo=FALSE, fig.width=8, fig.height=6}

p <- ggplot(gpCsumCode, aes(x=reorder(BNF.Chapter, -ITEMS), y=ITEMS)) +
  geom_bar(stat="identity", width=.5, fill="#E95420") +
  labs(title=paste0("Items by BNF Chapter - ","GP ",params$selgp, " - ",params$monthTitle),
       # subtitle=paste0("CCG ",params$selccg), 
       caption="source: NHS",
       x="BNF.Chapter") + 
    theme(plot.title = element_text(color="#333333"))+
scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 20))+
   scale_y_continuous()+
  theme(axis.text.x = element_text(size=9,angle=90, vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
p

```

### *Actual Costs*

**Actual costs by BNF code** for <span style="background-color:#33ff33"> *GP `r params$selgp`-`r params$monthTitle `*</span> are distributed as follows

```{r, echo=FALSE, fig.width=8, fig.height=6}
p <- ggplot(gpCsumCode, aes(x=reorder(BNF.Chapter, -ACT.COST), y=ACT.COST)) + 
  geom_bar(stat="identity", width=.5, fill="#E95420") + 
  labs(title=paste0("Actual costs by BNF Chapter - ","GP ",params$selgp, " - ",params$monthTitle),
       # subtitle="England", 
       caption="source: NHS",
       x="BNF.Chapter") + 
    theme(plot.title = element_text(color="#333333"))+
scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 20))+
   scale_y_continuous()+
  theme(axis.text.x = element_text(size=9,angle=90, vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
p
```

### *Prescribed quantity*

**Total prescribed quantity by BNF code** for <span style="background-color:#33ff33"> *GP `r params$selgp`-`r params$monthTitle `*</span> are distributed as follows

```{r, echo=FALSE, fig.width=8, fig.height=6}
p <- ggplot(gpCsumCode, aes(x=reorder(BNF.Chapter, -QUANTITY), y=QUANTITY)) + 
  geom_bar(stat="identity", width=.5, fill="#E95420") + 
  labs(title=paste0("Total quantity by BNF Chapter - ","GP ",params$selgp, " - ",params$monthTitle),
       # subtitle="England", 
       caption="source: NHS",
       x="BNF.Chapter") + 
    theme(plot.title = element_text(color="#333333"))+
scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 20))+
   scale_y_continuous()+
  theme(axis.text.x = element_text(size=9,angle=90, vjust=0.4, hjust=1))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0)))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0)))
p
```

## **Cost analysis**


The average NIC per 1K patients in the <span style="background-color:#33ff33"> *GP `r params$selgp`-`r params$monthTitle `*</span> is **`r round(gpSumC$NIC_RATE,2)`**. This value set the GP at the **`r names(which(gpSumC$NIC_RATE < quantile(gpSum$NIC_RATE, probs = seq(0, 1, by= 0.1)))[1])`** percentile of the CCG distribution for this indicator.

The figure below provides a graphical comparison of the CCG costs benchmarked with other CCG rates.

```{r, echo=FALSE, fig.width=8, fig.height=6}
ggplot(gpSum, aes(x= NIC_RATE, y= reorder(PRACTICE, NIC_RATE))) +
  geom_point(stat='identity', aes(col=NIC_RATE_Z_TYPE), size=2) +
  scale_color_manual(
    # labels = c("Cost Above Average", "Average Cost", "Cost Below Average","Cost for selected GP"),
    values = c("Cost Below Average"="#33ff33", "Average Cost"="#ffef00", "Cost Above Average" = "#E95420","Cost for selected GP" = "#00ffff")) +
  coord_flip()+
  ggtitle(paste0("Costs per 1K patients - GP ",params$selgp)) +
    theme(plot.title = element_text(color="#333333"))+
xlab("NIC per 1K patients") +
  ylab( "Practice") +
  theme(axis.text.x = element_blank())+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.ticks.x =element_blank())+
  # theme(axis.line.x =element_blank())+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))+
  theme(legend.position = "bottom")+
  theme(legend.title = element_blank())+
  theme(legend.text = element_text(size=9,color="#333333"))+
  geom_point(data=gpSumC , aes(x=NIC_RATE, y=PRACTICE), colour="#00FFFF", size=3)+
  geom_text(aes(label=ifelse(PRACTICE == params$selgp,round(NIC_RATE,3),'')),hjust=0,vjust=-0.8,size=3,color="#333333")


```

<span style="color:#E95420">------------------------------------------------------------------------------------------------------------------------------------------------------------------------------</span>

# Data source

Information on prescriptions have been obtained from NHS. Additional information on prescriptions can be found at this website https://digital.nhs.uk/data-and-information/publications/statistical/practice-level-prescribing-data.

All information are made available via the PrescRiption package.
